PHAT RAID, yo

### 2014-05-15 paper/paper.tex
intro

>>>>

Our setting is in a data center where we have low network latency,
high network throughput, and the need to store large files with tolerance to
some CPU, network, and disk failure. We reason that with these characteristics,
disk read/write latency will be the major factor in overall latency to store a file
with replication. As a result, we borrow ideas from RAID that allow for faster
disk access, and mix them with ideas for distributed consensus algorithms that
allow for consistent replication.
